\section*{\Huge Summary}
Robots operating in the real world must deal with uncertainty,
be it due to working with humans who are unpredictable, or simply 
because they must operate in a dynamic environment.
Ignoring the uncertainty could be dangerous, while accounting 
for all possible outcomes, as in contingent planning, is often 
computationally infeasible.
One possibility, which lies between ignoring the uncertainty 
completely and addressing it completely is to use flexible 
plans with choice, formulated as Temporal Planning Networks (TPNs).
This approach has been successfully demonstrated to work in 
human-robot teaming using the Pike executive, an online executive
that unifies intent recognition and plan adaptation.
However, one of the main challenges to using Pike is the need 
to manually specify the TPN. In this thesis, we address this 
challenge by describing a technique for automatically synthesizing 
a TPN which covers multiple possible executions for a given temporal
planning problem specified in PDDL 2.1. Our approach starts by
using a diverse planner to generate multiple plans, and then merges
them into a single TPN. As there were no available diverse planners
for temporal planning, we first show how to adapt existing 
diverse planning based on top-$k$ planning to the temporal 
setting. We then show how to merge the diverse plans into a
single TPN using constraint optimization. Finally, an empirical
evaluation on a set of IPC benchmarks shows that our approach
scales well, and generates TPNs which can generalize the set of
plans they are generated from.

\afterpage{\null\newpage}